### 2024-08-08 NN/plots_preds_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-97.09-Tanh1HiddenLayer-Impedance module.png}
    \caption{Prediction of Impedance module with Tanh1HiddenLayer - R-Squared: 0.93}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
\end{figure}
